Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
wip

\noindent
\textbf{Perfect Partition Learner algorithm.}
\maciek{There should be a description of the algoritm. What steps it takes. Instead, we have PPL's properties here, and the algorithm description is not present at all.}
Fix the initial partition
$P_I :=\{ I_1, \dots, I_{\ell}\}$ and \OPT's final partition
$P_F := \{F_1, \dots, F_{\ell}\}$.
The \emph{distance} of a~partition
 $P = \{C_1, \dots, C_{\ell}\}$ from the initial partition,
defined as 
$\Delta(P) := \sum_{j=1}^{\ell} | C_j \setminus I_j |$,
 is the number of nodes in $P$ that do not reside in their initial cluster.
In other words,
at least $\Delta(P)$ node migrations are required in order to reach the partition $P$ from $P_I$, and thus
$\OPT \geq \Delta^*:= \Delta(P_F) $ \maciek{Confusing. We have space. First define :=, then say that OPT bounds}.
%We  use $ \Delta(P_F) $ wherever the initial partition is clear from the context
The scheme of the algorithm can be found in the  appendix (Algorithm \ref{alg:ppl}).

@@

	Now we bound $\TAlg(\sigma_I)$.
	A~cluster of type $C_3$ contributes at most $3 \alpha - 1$ to $\TAlg(\sigma_I)$, as two pairs of nodes from the component are saturated and incurred the cost $\alpha$ each, and the third, unsaturated pair incurs the cost at most $\alpha-1$.
	Other cluster types contribute less: $C_1$ contributes~$0$ and $C_2$ contributes $\alpha$.
	Summing over all $\ell$ clusters gives us $\TAlg(\sigma_I) \leq (3 \alpha-1)\cdot \ell \leq 3\alpha\cdot\ell$.

>>>>

\noindent
\textbf{Perfect Partition Learner algorithm.}
\maciek{There should be a short description of the algorithm: what steps it takes, how it treats the input. Instead, we have PPL's properties here, and the algorithm description is not present at all.}
Fix the initial partition
$P_I :=\{ I_1, \dots, I_{\ell}\}$ and \OPT's final partition
$P_F := \{F_1, \dots, F_{\ell}\}$.
The \emph{distance} of a~partition
 $P = \{C_1, \dots, C_{\ell}\}$ from the initial partition,
defined as 
$\Delta(P) := \sum_{j=1}^{\ell} | C_j \setminus I_j |$,
 is the number of nodes in $P$ that do not reside in their initial cluster.
In other words,
at least $\Delta(P)$ node migrations are required in order to reach the partition $P$ from $P_I$, and thus
$\OPT \geq \Delta^*:= \Delta(P_F) $ \maciek{Confusing. We have space. First define :=, then say that OPT bounds}.
%We  use $ \Delta(P_F) $ wherever the initial partition is clear from the context
The scheme of the algorithm can be found in the  appendix (Algorithm \ref{alg:ppl}).

@@

	Now we bound $\TAlg(\sigma_I)$ by summing the intra-component counters of each cluster at the end of the phase.
	The sum of intra-component counters in a cluster of type $C_3$ is at most $3 \alpha - 1$: two pairs of nodes from the component are saturated and its counter is $\alpha$ each, and the counter of the third, unsaturated pair is at most $\alpha-1$.
	The sum of counters inside $C_1$ is $0$, and inside $C_2$ it is $\alpha$.
	Summing over all $\ell$ clusters gives us $\TAlg(\sigma_I) \leq (3 \alpha-1)\cdot \ell \leq 3\alpha\cdot\ell$.
